---
title: "msb106_assignment"
format: html
editor: visual
---

# Evolving Landscapes: Analysing the Dynamics of Urban and Rural Development in Europe

**MSB106 Anvendt by- og regionaløkonomi\
Assignment Spring 2024**

**Hanna Sundal Bjerkreim, Ingrid Strømme og Emilie Hansen Sørhaug**

The aim of this assignment is to provide an understanding of some of the potential drivers contributing to the urban-rural divide in Europe.
We will delve into the influence of factors shaping this division, such as local labour market conditions, affect patterns of population distribution and job creation across different European landscapes.

```{r}
#| label: setup 
#| output: false
#| message: false
library(tidyverse)
library(readxl)
library(dplyr)
library(ggplot2)
```

## Part 1: Data Collection and Initial Analysis

The first part presents an overview of the data collection process, followed by an analysis of the population growth dynamics in various European regions.

### Task 1 -- Data Gathering

```{r}
data <- read_csv("ilc_lvho01__custom_9371289_linear.csv", 
    locale = locale(date_names = "nb", encoding = "ISO-8859-1"))
View(ilc_lvho01_custom_9371289_linear)
```

```{r}
columns_to_remove <- c("DATAFLOW", "LAST UPDATE", "freq", "incgrp", "building", "unit", "OBS_FLAG")
data <- data[, !(names(data) %in% columns_to_remove)]
```

```{r}
# Endre verdier i kolonnen "deg_urb"
data <- data %>% 
  mutate(deg_urb = case_when(
    deg_urb == "DEG1" ~ "Cities",
    deg_urb == "DEG2" ~ "Towns/Suburbs",
    deg_urb == "DEG3" ~ "Rural areas",
    TRUE ~ deg_urb  # Hvis ingen av de over er oppfylt, behold eksisterende verdi
  ))
```

```{r}
print(unique(data$deg_urb))
```

```{r}
cities_plot <- data |>
  filter(deg_urb == "Cities") |>
  ggplot(aes(x = "TIME_PERIOD", y = "OBS_VALUE")) +
  geom_line() +
  labs(title = "Population Growth Trends in Cities",
       x = "Year",
       y = "Population Growth")
```

### Task 2 -- Data Analysis

## Part 2: Advanced Analysis - Understanding the Impact of Economic Factors on Population Growth

In the second part, we will extend the data collected in the first part by incorporating additional economic factors.
Our analysis will focus on how these factors correlate with population growth in different regions, employing the classification methodology detailed in Chapter 5 of Andersson, Håkansson, and Thorsen (2023).

### Task 1 - Gathering Additional Data

### Task 2 - Application of Classification Methodology

### Task 3 - Analysis and Visualization

### Task 4 - Interpretation and Relation to Course Literature
